Notes for Week 2/8/19 - 2/15/19

### 2019-02-15 notes/reference_notes/padilla18.tex
added updated version of this week's notes and notes on references

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}

@@

The assumptions required for Theorems \ref{thm: padilla18_theorem_1} and \ref{thm: padilla18_theorem_2} are as follows.
\begin{enumerate}[(a)]
	\item For all $x \in \Xset$
	\begin{equation*}
	0 < p_{\min} \leq p(x) \leq p_{\max} < \infty
	\end{equation*}
	\item The base measure $\mu$ in $\Xset$ satisfies
	\begin{equation*}
	r^d c_{1,d} \leq \mu(B_r(x)) \leq c_{2,d} r^d \tag{$\forall x \in \Xset$}
	\end{equation*}
	\item There exists a homeomorphism (continuous bijection with continuous inverse) $h: \Xset \to [0,1]^d$ such that
	\begin{equation*}
	L_{\min} d_{\Xset}(x,x') \leq \norm{h(x) - h(x')}_2  \leq L_{\max} d_{\Xset}(x,x') \tag{$\forall x,x' \in \Xset$}
	\end{equation*}
	\item The function $g_0 := f_0 \circ h^{-1}$ has bounded variation, meaning
	\begin{equation*}
	\abs{g_0}_{BV(\Omega)} := \sup \set{\int_{\Omega} g_0(x) \dive(g)(x)dx; g \in C_c^1(\Omega, \Rd), \norm{g}_{\infty} \leq 1} < \infty
	\end{equation*}
	where $\mathfrak{B}$ is the Borel $\sigma$-algebra of $\Omega = [0,1]^d$, $C_c^1(\Omega, \Rd)$ is the set of $\mathfrak{B}$-measurable, continuously differentiable functions into $\Rd$, and
	\begin{equation*}
	\norm{g}_{\infty} := \norm{\left(\sum_{i=1}^{d}g_i^2\right)^{1/2}}_{L_{\infty}(\Omega)}.
	\end{equation*}
	\item $g_0$ is piecewise Lipschitz\footnote{Technically, the requirement is slightly weaker than piecewise Lipschitz.}, meaning there exists a set $\Sset \subset (0,1)^d$ such that
	\begin{enumerate}
		\item $\nu(\Sset) = 0$.
		\item $\mu\Bigl( h^{-1}\bigl(S_{\epsilon} \cup ([0,1]^d \setminus \Omega_{\epsilon})\bigr) \Bigr) \leq C_{\Sset} \epsilon$
		\item There exists a positive constant $L_0$ such that if $z$ and $z'$ belong to the same connected component of $\Omega_{\epsilon} \setminus B_{\epsilon}(\Sset)$, then 
		\begin{equation*}
		\abs{g(z) - g(z')} \leq L_0 \norm{z - z'}_2
		\end{equation*}
	\end{enumerate}
	where $\Omega_{\epsilon} = [0,1]^d \setminus B_{\epsilon}(\partial [0,1]^d)$.
\end{enumerate}

@@

\section{Proof of Theorem \ref{thm: padilla18_theorem_1}}

@@

\begin{lemma}
	Fix $N$ to satisfy \eqref{eqn: N_lower_bound}, and let us assume that the event $\Omega$ from Lemma \ref{lem: mesh_counts} holds. Denote $I = P_{lat}(N)$ to be the mesh. Then, for all $e \in \Reals^n$, it holds that
	\begin{equation*}
	\abs{e^T(\theta - \theta_I)} \leq 2 \norm{e}_{\infty} \norm{\nabla_{G_K} \theta}_1, \tag{$\forall \theta \in \Reals^n$}
	\end{equation*}
	Moreover, 
	\begin{equation*}
	\norm{D \theta^I}_1 \leq \norm{\nabla_{G_K} \theta}_1, \tag{$\forall \theta \in \Reals^n$}
	\end{equation*}
	where $D$ is the incidence matrix of $G_{lat}$.
\end{lemma}

>>>>

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\1}{\mathbb{I}}

@@

The assumptions required for Theorems \ref{thm: padilla18_theorem_1} and \ref{thm: padilla18_theorem_2} are as follows.
\begin{enumerate}[(a)]
	\item For all $x \in \Xset$
	\begin{equation*}
	0 < p_{\min} \leq p(x) \leq p_{\max} < \infty
	\end{equation*}
	\item The base measure $\mu$ in $\Xset$ satisfies
	\begin{equation*}
	r^d c_{1,d} \leq \mu(B_r(x)) \leq c_{2,d} r^d \tag{$\forall x \in \Xset$}
	\end{equation*}
	\item There exists a homeomorphism (continuous bijection with continuous inverse) $h: \Xset \to [0,1]^d$ such that
	\begin{equation*}
	L_{\min} d_{\Xset}(x,x') \leq \norm{h(x) - h(x')}_2  \leq L_{\max} d_{\Xset}(x,x') \tag{$\forall x,x' \in \Xset$}
	\end{equation*}
	\item $g_0$ is piecewise Lipschitz\footnote{Technically, the requirement is slightly weaker than piecewise Lipschitz.}, meaning there exists a set $\Sset \subset (0,1)^d$ such that
	\begin{enumerate}
		\item $\nu(\Sset) = 0$.
		\item $\mu\Bigl( h^{-1}\bigl(S_{\epsilon} \cup ([0,1]^d \setminus \Omega_{\epsilon})\bigr) \Bigr) \leq C_{\Sset} \epsilon$
		\item There exists a positive constant $L_0$ such that if $z$ and $z'$ belong to the same connected component of $\Omega_{\epsilon} \setminus B_{\epsilon}(\Sset)$, then 
		\begin{equation*}
		\abs{g(z) - g(z')} \leq L_0 \norm{z - z'}_2
		\end{equation*}
	\end{enumerate}
	where $\Omega_{\epsilon} = [0,1]^d \setminus B_{\epsilon}(\partial [0,1]^d)$.
\end{enumerate}

@@

\section{Proofs}

@@

\begin{lemma}
	\label{lem: quantization_error}
	Fix $N$ to satisfy \eqref{eqn: N_lower_bound}, and let us assume that the event $\Omega$ from Lemma \ref{lem: mesh_counts} holds. Denote $I = P_{lat}(N)$ to be the mesh. Then, for all $e \in \Reals^n$, it holds that
	\begin{equation*}
	\abs{e^T(\theta - \theta_I)} \leq 2 \norm{e}_{\infty} \norm{\nabla_{G_K} \theta}_1, \tag{$\forall \theta \in \Reals^n$}
	\end{equation*}
	Moreover, 
	\begin{equation*}
	\norm{D \theta^I}_1 \leq \norm{\nabla_{G_K} \theta}_1, \tag{$\forall \theta \in \Reals^n$}
	\end{equation*}
	where $D$ is the incidence matrix of $G_{lat}$.
\end{lemma}
\begin{proof}
	Clearly
	\begin{equation*}
	\dotp{\epsilon^T}{\theta - \theta_{I}} \leq \norm{\epsilon}_{\infty} \cdot \norm{\theta - \theta_I}_1
	\end{equation*}
	Then, for every $i = 1, \ldots, n$, the event $\Omega$ implies that there exists a $j \in [n]$ such that
	\begin{equation*}
	(\theta_I)_i = \theta_j,~~ (x_i,x_j) \in E_{G_K}
	\end{equation*}
	and therefore
	\begin{equation*}
	\norm{\theta - \theta_I}_1 \leq \norm{\nabla_{G_K} \theta}_1
	\end{equation*}
\end{proof}

\subsection{Bounding empirical process}

\begin{lemma}
	Conditional on the event $\Omega$, we have that
	\begin{equation*}
	\dotp{\epsilon}{\widehat{\theta}_I - \widehat{\theta}_I^{\star}} \leq \max_{u \in I} \sqrt{\abs{C(u)}} \left( \norm{\Pi \widetilde{\epsilon}}_2 \norm{\widehat{\theta} - \theta^{\star}}_2  + \norm{(D^{\dagger})^T \widetilde{\epsilon}}_{\infty} \left[ \norm{\nabla_{G_K} \widehat{\theta} }_1 + \norm{\nabla_{G_K} \theta^{\star} }_1  \right]\right)
	\end{equation*}
	where $\widetilde{\epsilon}$ is an independent, mean-zero vector of subgaussian random variables, $\abs{C(u)} := \sum_{i \in [n]} \1(x_i \in C(u))$, and $D^{\dagger}$ is the pseudoinverse of the incidence matrix $D$ of $G_{lat}$.
\end{lemma}
\begin{proof}
	Writing
	\begin{equation*}
	\widetilde{\epsilon}_l = \left[\max_{u \in I} \abs{C(u)} \right]^{-1/2} \sum_{x_j \in I_l} \epsilon_j
	\end{equation*}
	we have
	\begin{align*}
	\dotp{\epsilon}{\widehat{\theta}_I - \theta_I^{\star}} = \left[\max_{u \in I} \abs{C(u)}\right]^{1/2} \dotp{\widetilde{\epsilon}}{\widehat{\theta}^{I} - \theta^{\star,I}}
	\end{align*}
	Now, divide up $\widetilde{\epsilon}$ into 
	\begin{equation*}
	\widetilde{\epsilon} = P_{1}(\widetilde{\epsilon}) + P_{1^{\perp}}(\widetilde{\epsilon})
	\end{equation*}
	where $P_1$ is the projection onto the span of $\mathbf{1}$ the constant vector, and $P_{1^{\perp}}$ the projection onto the space orthogonal to $\mathbf{1}$. Note that $P_{1^{\perp}}(x) = (D^{\dagger} D)^T x$. Then, we have
	\begin{align*}
	\dotp{P_{1^{\perp}}(\widetilde{\epsilon})}{\widehat{\theta}^{I} - \theta^{\star,I}} & = \dotp{(D^{\dagger} D)^T \widetilde{\epsilon}}{\widehat{\theta}^{I} - \theta^{\star,I}} \\
	& = \dotp{(D^{\dagger})^T \widetilde{\epsilon}}{D(\widehat{\theta}^{I} - \theta^{\star,I})} \\
	& \leq \norm{(D^{\dagger})^T \widetilde{\epsilon}}_{\infty} \norm{ D(\widehat{\theta}^{I} - \theta^{\star,I})  }_1
	& \leq \norm{(D^{\dagger})^T \widetilde{\epsilon}}_{\infty} \left[ \norm{\nabla_{G_K} \widehat{\theta} }_1 + \norm{\nabla_{G_K} \theta^{\star} }_1 \right]
	\end{align*}
	where the last inequality follows from the triangle inequality and Lemma \ref{lem: quantization_error}.

	On the other hand,
	\begin{equation*}
	\dotp{P_{1}(\widetilde{\epsilon})}{\widehat{\theta}^{I} - \theta^{\star,I}} \leq \norm{P_{1}(\widetilde{\epsilon})}_2 \norm{\widehat{\theta}^{I} - \theta^{\star,I}}_2
	\end{equation*}
	and so the desired result follows.
\end{proof}

\subsection{Proof of Theorem \ref{thm: padilla18_theorem_1}}
We begin with a basic inequality
\begin{equation*}
\frac{1}{2} \norm{\widehat{\theta} - \theta^*}_n^2 \leq \frac{1}{n} \dotp{\epsilon}{\widehat{\theta} - \theta^{\star}} + \lambda_n \left(\norm{\nabla_G \theta^*}_1 - \norm{\nabla_G \widehat{\theta}}_1 \right)
\end{equation*}

We split up the \textcolor{red}{empirical process},
\begin{equation*}
\dotp{\epsilon}{\widehat{\theta} - \theta^{\star}} = \dotp{\epsilon}{\widehat{\theta} - \widehat{\theta}_I} + \dotp{\epsilon}{\widehat{\theta}_I - \theta_I^{\star}} + \dotp{\epsilon}{\theta_I^{\star} - \theta^{\star}}
\end{equation*}
Hereafter in the proof, we condition on the event $\Omega$. Lemma \ref{lem: quantization_error} gives us bounds on the first and third terms
\begin{align*}
\dotp{\epsilon}{\widehat{\theta} - \widehat{\theta}_I} & \leq 2 \norm{\epsilon}_{\infty} \cdot \norm{\nabla_{G_K} \widehat{\theta} }_1 \\
\dotp{\epsilon}{\theta^{\star} - \theta_I^{\star}} & \leq 2 \norm{\epsilon}_{\infty} \cdot \norm{\nabla_{G_K} \theta^{\star} }_1
\end{align*}

### 2019-02-15 notes/weekly_notes/2.14.19.NotesForWeek.tex
added updated version of this week's notes and notes on references

Consider $\Xbf = (X_1, \ldots, X_n) \sim \Pbb$ and $\Ybf = (Y_1, \ldots, Y_m) \sim \Qbb$ independently generated random variables. We will assume $\Pbb$ and $\Qbb$ are supported on $\D \subset \Reals^d$ and are absolutely continuous with density functions $f$ and $g$, respectively. Our statistical goal is hypothesis testing: that is, we wish to construct a test function $\phi$ which differentiates between
\begin{equation*}
\mathbb{H}_0: f = g \text{ and } \mathbb{H}_1: f \neq g.
\end{equation*}

For a given function class $\Hclass$, some $\epsilon > 0$, and test function $\phi$ a Borel measurable function of the data with range $\set{0,1}$, we evaluate the quality of the test using \emph{worst-case risk}
\begin{equation*}
R_{\epsilon}^{m,n}(\phi; \Hclass) = \sup_{f \in \Hclass} \Ebb_{f,f}^{(m,n)}(\phi) + \sup_{ \substack{f,g \in \Hclass \\ \delta(f,g) \geq \epsilon } } \Ebb_{f,g}^{m,n}(1 - \phi)
\end{equation*}

@@

Let $\Zbf = (X_1, \ldots, X_n, Y_1, \ldots, Y_m)$, and let $t = n + m$. As in \citep{padilla2018}, define the \emph{$K$-NN graph} $G_K = (V,E_K)$ to have vertex set $V = \set{1, \ldots, t}$ and edge set $E_K$ which contains the pair $(i,j)$ if and only if $x_i$ is among the $K$-nearest neighbors (with respect to Euclidean distance) of $x_j$, or vice versa. Let $D_K$ denote the incidence matrix of $G_K$.

Define the \emph{kNN-total variation} test statistic to be
\begin{equation}
\label{eqn: knn_tv_test_statistic}
T_{TV} = \sup_{\substack{\theta \in \Reals^{t}: \\ \norm{D_{k} \theta}_1 \leq C_{n,k}} } \left(\sum_{i = 1}^{n} \theta_i - \sum_{j = n+1}^{t} \theta_j\right)
\end{equation}

@@

\begin{conjecture}
	For $\tau = ???$ and $K \asymp \log^{1 + 2r}(n)$ for some $r \geq 0$, the test $\phi_{TV} = \set{T_{TV} \geq \tau}$ has worst-case risk
	\begin{equation*}
	R_{\epsilon}^{(m,m)}(\Hclass_{lip}(L)) \leq c_1/a^2
	\end{equation*}
	whenever $\epsilon \geq c_2 a \log^{\alpha}m m^{-1/d}$ where $\alpha = 3r + 5/2 + (2r + 1)/d$ and $c_1$ and $c_2$ are constants which depend only on $(d,L)$.
\end{conjecture}
\begin{proof}
	Write
	\begin{equation*}
	\sum_{i = 1}^{m} \theta_i - \sum_{j = m + 1}^{2m} \theta_j = \dotp{\theta}{1_X - 1_Y}
	\end{equation*}
	where
	\begin{equation*}
	1_X = 
	\begin{cases}
	1,~ i = 1, \ldots,m \\
	0,~ \text{otherwise}
	\end{cases}
	1_Y = 
	\begin{cases}
	1,~ i = j + 1, \ldots,2m \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}
	Let
	\begin{equation*}
	\widehat{\theta} \in \argmax_{\theta \in \Reals^{2m}} \set{\dotp{\theta}{1_X - 1_Y}: \norm{D_K \theta}_1 \leq C_{n,k}}
	\end{equation*}
	satisfy $T_{TV} = \dotp{\widehat{\theta}}{1_X - 1_Y}$. For $i = 1, \ldots, 2m$, introduce $\theta^{\star}$ defined by
	\begin{equation*}
	(\theta^{\star})_i = \left(\frac{f(z_i) - g(z_i)}{f(z_i) + g(z_i)} \right)	\end{equation*}

@@

	We bound the first term, and begin by employing a basic inequality argument. Let
	\begin{align*}
	\widetilde{\theta} = \frac{\theta^{\star}}{\norm{D\theta^{\star}}_1}.
	\end{align*}
	Since $\widetilde{\theta}$ is feasible and $\widehat{\theta}$ optimal for \eqref{eqn: knn_tv_test_statistic}, we have
	\begin{equation*}
	\dotp{\widehat{\theta}}{1_X - 1_Y} \geq \dotp{\widetilde{\theta}}{1_X - 1_Y}
	\end{equation*}
	which, letting $w = (1_X - 1_Y) - \theta^{\star}$, means
	\begin{equation}
	\label{eqn: basic_inequality_1}
	\dotp{\widehat{\theta}}{\theta^{\star}} \geq \dotp{\widetilde{\theta}}{\theta^{\star}} - \dotp{\widehat{\theta} - \widetilde{\theta}}{w}
	\end{equation}

	As a result, we have
	\begin{align*}
	\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}} & \leq \abs{\dotp{\widehat{\theta} - \theta^{\star}}{\theta^{\star}} } + \abs{\dotp{\widehat{\theta} - \theta^{\star}}{w} } \\
	& \overset{(i)}{\leq} \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + \abs{\dotp{\widehat{\theta} - \widetilde{\theta}}{w} } + \abs{\dotp{\widehat{\theta} - \theta^{\star}}{w} } \\
	& \leq \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + 2\abs{\dotp{\widehat{\theta} - \widetilde{\theta}}{w} } + \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{w}}
	\end{align*}
	where $(i)$ follows from \eqref{eqn: basic_inequality_1}.
\end{proof}

>>>>

Consider distributions $\Pbb$ and $\Qbb$ supported on $\D \subset \Reals^d$ which are absolutely continuous with density functions $f$ and $g$, respectively. For fixed $t \geq 0$, Let $\Zbf = (z_1, \ldots,z_t)$, where for $i = 1,\ldots,t$, $z_i \sim \frac{\Pbb + \Qbb}{2}$ are independent. Given $\Zbf$, for $i = 1,...,t$ let
\begin{equation*}
\ell_i = 
\begin{cases}
1~ \text{with probability $\frac{f(z_i)}{f(z_i) + g(z_i)}$} \\
-1~ \text{with probability $\frac{g(z_i)}{f(z_i) + g(z_i)}$}
\end{cases}
\end{equation*} 
be conditional independent labels, and write
\begin{equation*}
1_X = 
\begin{cases}
1,~ l_i = 1\\
0,~ \text{otherwise}
\end{cases}
1_Y = 
\begin{cases}
1,~ l_i = -1 \\
0,~ \text{otherwise.}
\end{cases}
\end{equation*}
We will write $\Xbf = \set{x_1, \ldots,x_{N_1}} := \set{z_i: \ell_i = 1}$ and similarly $\Ybf = \set{y_1, \ldots,y_{N_2}} := \set{y_i: \ell_i = -1}$, where $N_1$ and $N_2$ are random.

Our statistical goal is hypothesis testing: that is, we wish to construct a test function $\phi$ which differentiates between
\begin{equation*}
\mathbb{H}_0: f = g \text{ and } \mathbb{H}_1: f \neq g.
\end{equation*}

For a given function class $\Hclass$, some $\epsilon > 0$, and test function $\phi$ a Borel measurable function of the data with range $\set{0,1}$, we evaluate the quality of the test using \emph{worst-case risk}
\begin{equation*}
R_{\epsilon}^{(t)}(\phi; \Hclass) = \sup_{f \in \Hclass} \Ebb_{f,f}^{(t)}(\phi) + \sup_{ \substack{f,g \in \Hclass \\ \delta(f,g) \geq \epsilon } } \Ebb_{f,g}^{(t)}(1 - \phi)
\end{equation*}

@@

As in \citep{padilla2018}, define the \emph{$K$-NN graph} $G_K = (V,E_K)$ to have vertex set $V = \set{1, \ldots, t}$ and edge set $E_K$ which contains the pair $(i,j)$ if and only if $x_i$ is among the $K$-nearest neighbors (with respect to Euclidean distance) of $x_j$, or vice versa. Let $D_K$ denote the incidence matrix of $G_K$.

Define the \emph{kNN-total variation} test statistic to be
\begin{equation}
\label{eqn: knn_tv_test_statistic}
T_{TV} = \sup_{\substack{\theta \in \Reals^{t}: \\ \norm{D_{k} \theta}_1 \leq C_{n,k}} } \left(\sum_{i: (1_X)_i = 1} \theta_i - \sum_{j:(1_Y)_j = 1} \theta_j\right)
\end{equation}

@@

\begin{conjecture}
	For $\tau = ???$ and $K \asymp \log^{1 + 2r}(n)$ for some $r \geq 0$, the test $\phi_{TV} = \set{T_{TV} \geq \tau}$ has worst-case risk
	\begin{equation*}
	R_{\epsilon}^{(t)}(\Hclass_{lip}(L)) \leq c_1/a^2
	\end{equation*}
	whenever $\epsilon \geq c_2 a \log^{\alpha}m m^{-1/d}$ where $\alpha = 3r + 5/2 + (2r + 1)/d$ and $c_1$ and $c_2$ are constants which depend only on $(d,L)$.
\end{conjecture}
\begin{proof}
	Write
	\begin{equation*}
	\left(\sum_{i: (1_X)_i = 1} \theta_i - \sum_{j:(1_Y)_j = 1} \theta_j\right) = \dotp{\theta}{1_X - 1_Y}
	\end{equation*}
	and let
	\begin{equation*}
	\widehat{\theta} \in \argmax_{\theta \in \Reals^{2m}} \set{\dotp{\theta}{1_X - 1_Y}: \norm{D_K \theta}_1 \leq C_{n,k}}
	\end{equation*}
	satisfy $T_{TV} = \dotp{\widehat{\theta}}{1_X - 1_Y}$. For $i = 1, \ldots, 2m$, introduce $\theta^{\star}$ defined by
	\begin{equation*}
	(\theta^{\star})_i = \left(\frac{f(z_i) - g(z_i)}{f(z_i) + g(z_i)} \right)	\end{equation*}

@@

	 Let
	\begin{align*}
	\widetilde{\theta} = \frac{\theta^{\star}}{\norm{D\theta^{\star}}_1}.
	\end{align*}
	We bound the first term, dividing into two cases.
	\paragraph{Case 1:} First, suppose $\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}} \geq \norm{\theta - \widetilde{\theta}}_2^2$.

	We begin by employing a basic inequality argument.
	Since $\widetilde{\theta}$ is feasible and $\widehat{\theta}$ optimal for \eqref{eqn: knn_tv_test_statistic}, we have
	\begin{equation*}
	\dotp{\widehat{\theta}}{1_X - 1_Y} \geq \dotp{\widetilde{\theta}}{1_X - 1_Y}
	\end{equation*}
	which, letting $w = (1_X - 1_Y) - \theta^{\star}$, means
	\begin{equation}
	\label{eqn: basic_inequality_1}
	\dotp{\widehat{\theta}}{\theta^{\star}} \geq \dotp{\widetilde{\theta}}{\theta^{\star}} - \dotp{\widehat{\theta} - \widetilde{\theta}}{w}
	\end{equation}

	As a result, we have
	\begin{align*}
	\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}} & \leq \abs{\dotp{\widehat{\theta} - \theta^{\star}}{\theta^{\star}} } + \abs{\dotp{\widehat{\theta} - \theta^{\star}}{w} } \\
	& \overset{(i)}{\leq} \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + \abs{\dotp{\widehat{\theta} - \widetilde{\theta}}{w} } + \abs{\dotp{\widehat{\theta} - \theta^{\star}}{w} } \\
	& \leq \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + 2\abs{\dotp{\widehat{\theta} - \widetilde{\theta}}{w} } + \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{w}}
	\end{align*}
	where $(i)$ follows from \eqref{eqn: basic_inequality_1}.

	$w$ are mean-zero, bounded random variables, and are therefore subgaussian with parameter $2$. Then, from \citep{padilla2018}, we have
	\begin{lemma}[Approximate restatement of \citep{padilla2018}]
		\begin{equation}
		\label{eqn: empirical_process_lower_bound}
		\abs{\dotp{\widehat{\theta} - \theta^{\star}}{w}} \lesssim \sqrt{K \log n} \left[ \norm{D_K \widetilde{\theta}}_1 + \norm{D_K \widehat{\theta}} \right] + \sqrt{K} \cdot \left(\norm{\widehat{\theta} - \widetilde{\theta}}_2 \right)
		\end{equation}
		with probability at least 
		\begin{equation*}
		\Omega \left(1 - \frac{n}{K} \exp\left(-K\right) - n \exp(-K)  \right)
		\end{equation*}
	\end{lemma}
	Condition on the event of \eqref{eqn: empirical_process_lower_bound} holding. As a result, we have
	\begin{align*}
	\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}} & \lesssim  \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + \sqrt{K \log n} \left[ \norm{D_K \widetilde{\theta}}_1 + \norm{D_K \widehat{\theta}} \right] + \sqrt{K} \cdot \left(\norm{\widehat{\theta} - \widetilde{\theta}}_2 \right) \\
	& \leq \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + \sqrt{K \log n} \left[ \norm{D_K \widetilde{\theta}}_1 + \norm{D_K \widehat{\theta}} \right] + \sqrt{K} \cdot \left(\sqrt{\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}}} \right)
	\end{align*}
	which, along with the inequality $ab - b^2/4 \leq a^2$, implies
	\begin{equation*}
	\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}} \leq \abs{\dotp{\widetilde{\theta} - \theta^{\star}}{\theta^{\star}} } + \sqrt{K \log n} \left[ \norm{D_K \widetilde{\theta}}_1 + \norm{D_K \widehat{\theta}} \right] + K
	\end{equation*}

	\textcolor{red}{Continue from here.}

	\paragraph{Case 2:} Otherwise, we may assume $\abs{\dotp{\widehat{\theta} - \theta^{\star}}{1_X - 1_Y}} \leq \norm{\theta - \widetilde{\theta}}_2^2$.

	To upper bound $\norm{\theta - \widetilde{\theta}}_2^2$, we use the relation
	\begin{equation*}
	\dotp{\widehat{\theta}}{1_X - 1_Y} \leq  \dotp{\widetilde{\theta}}{1_X - 1_Y}
	\end{equation*}
	and therefore
	\begin{equation*}
	\norm{\widehat{\theta} - (1_X - 1_Y)}_2^2 \leq \norm{\widetilde{\theta} - (1_X - 1_Y)}_2^2 + \left(\norm{\widehat{\theta}}_2^2 - \norm{\widetilde{\theta}}_2^2\right)
	\end{equation*}

	\textcolor{red}{Continue from here using standard basic inequality + Poincare bound on the second term.}

\end{proof}
